An agent-based model of military mechanization

### 2018-07-08 paper2/paper2.tex
sources

>>>>

Methodology studies
\citep{pepinsky2005agents,de2014agent,gunitsky2013complexity,bousquet2011beyond,harrison2012complexity,jervis1998system,modelski1990world,modelski1999long}

Insurgency studies
\citep{cioffi2010mason,weidmann2013violence,bhavnani2012modeling,bhavnani2014group}

Big IR \citep{cederman2010growing,earnest2008coordination,masad2016dissertation}

Fundamentals, e.g. cooperation \citep{axelrod1981evolution}

Just because \citep{epstein1996growing}

Maybe it's because states are not unitary. Not necessariy requirement: e.g.,
household is agent in Schelling model.
